%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Quality Engineering Manager} % Job title
    {Spiralyze LLC} % Organization
    {Atlanta, GA - Remote} % Location
    {March 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Oversee the entire quality engineering department, setting strategic direction and goals aligned with company objectives.}
        \item {Develop and implement comprehensive quality assurance strategies, policies, and procedures to ensure product excellence.}
        \item {Lead and mentor a team of quality engineering professionals, fostering a culture of continuous improvement and innovation.}
        \item {Collaborate with senior leadership and cross-functional teams to drive quality initiatives and ensure product reliability and customer satisfaction.}
        \item {Manage resource allocation, budget, and project timelines to optimize team performance and deliver high-quality products on schedule.}
        \item {Continuously evaluate and adopt new tools, technologies, and methodologies to enhance testing capabilities and efficiency.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Quality Engineering Lead} % Job title
    {Spiralyze LLC} % Organization
    {Atlanta, GA - Remote} % Location
    {June 2019 - March 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a team of quality engineers, providing guidance and mentorship to ensure effective and efficient testing processes.}
        \item {Defined and implemented quality assurance best practices, standards, and metrics to measure and improve team performance.}
        \item {Coordinated testing efforts across multiple projects, ensuring consistent quality and timely delivery.}
        \item {Collaborated with stakeholders to define quality objectives and ensure alignment with overall business goals.}
        \item {Managed defect tracking and resolution processes, ensuring high-priority issues were addressed promptly.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Quality Engineer} % Job title
    {Spiralyze LLC} % Organization
    {Atlanta, GA - Remote} % Location
    {February 2018 - June 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and implemented comprehensive test plans and strategies for various software projects.}
        \item {Conducted functional, regression, and performance testing to ensure product quality and reliability.}
        \item {Collaborated with cross-functional teams, including development, product management, and operations, to ensure alignment on quality objectives.}
        \item {Analyzed test results and provided detailed feedback to the development team, driving continuous improvement in product quality.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {Web and Mobile Tester} % Job title
  {Digital Interpretations Scandinavia AB} % Organization
  {Stockholm, SE - Remote} % Location
  {July 2017 - February 2018} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Tested web and mobile applications across different platforms and browsers to ensure compatibility and performance.}
      \item {Created and maintained detailed test documentation, including test cases, test scripts, and test reports.}
      \item {Worked closely with developers and product managers to understand new features and enhancements, integrating them into test plans.}
      \item {Reported and tracked defects using issue tracking tools, ensuring prompt resolution by the development team.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
    {QA Tester} % Job title
    {SweatWorks} % Organization
    {Arlington, VA - Remote} % Location
    {January 2014 - July 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted thorough testing of software applications to identify and resolve bugs, ensuring high-quality product releases.}
        \item {Developed and executed test plans, test cases, and test scripts for various applications.}
        \item {Collaborated with development and product teams to understand requirements and design comprehensive test strategies.}
        \item {Utilized automated testing tools to enhance test coverage and efficiency.}
        \item {Documented and reported defects using bug tracking systems, ensuring timely resolution.}
        \item {Participated in user acceptance testing (UAT) and provided feedback to improve usability and functionality.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
